Discrete Quantum Theories and Computing

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex

\affiliation{Department of Computer Science, Indiana University, Bloomington,
Indiana 47405, USA}

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Why a \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic QIVPM is
Impossible?}

To illustrate our proof for non-existence of $\delta$-deterministic
QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
\end{cases}
\end{equation}
However, since we know that $0$-deterministic QIVPMs do not exist~\cite{THOS2017},
the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
is indeed a QIVPM. Since the range of $\bar{\mu}^{\textrm{D}}$, $\left\{ \imposs,\necess\right\} $,
is a set of singleton sets, if $\bar{\mu}^{\textrm{D}}$ satisfies
that for orthogonal projectors $P_{0}$ and~$P_{1}$, 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
\end{equation}
then we can apply the same reason of proving classical inclusion-exclusion
principle to get for each pair of \emph{commuting} projectors $P_{0}$
and~$P_{1}$, 
\[
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)
\]
which implies $\bar{\mu}^{\textrm{D}}$ is convex, i.e., $\bar{\mu}^{\textrm{D}}$
is a QIVPM. Therefore, our task now is to prove Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal}).

@@

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}
\end{figure*}

For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
$\bar{\mu}\left(P_{0}\right)\subseteq\left[\frac{3}{4},1\right]$,
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$,
and $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},\frac{5}{4}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.

For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

\section{\texorpdfstring{$\frac{1}{4}$}{¼}-deterministic Classical IVPM}

@@

Although the definition of $\delta$-determinism in our paper only
applied to QIVPMs~\cite{THOS2017}, this definition can be easily
extended to apply to both classical and quantum IVPMs as follow.

\begin{definition}[$\delta$-Determinism]\label{def:delta-deterministic}
Given a classical or quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
where $\events'$ is the set of all events, $\events$, when $\bar{\mu}$
is a QIVPM and $\events'$ is the set of mutually commuting events,
$\eventsC$, when $\bar{\mu}$ is a classical one. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent It is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always comes up heads. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
to double-headed (or double-tailed), which we can certainly know the
outcome of a coin even before tossing. We see here that we can construct
$0$-deterministic as well as $\frac{1}{4}$-deterministic and in
fact for any $\delta$ in the range $\left[0,1\right]$ we can construct
a $\delta$-deterministic classical probability measure. BUT the situation
changes in the quantum case, WE CANNOT construct $\delta$-deterministic
probability measures for $\delta<\frac{1}{3}$.

\section{Why a \texorpdfstring{$\frac{1}{3}$}{⅓}-deterministic QIVPM exists?}

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex

\date{\today}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Why a \texorpdfstring{$\frac{1}{4}$}{¼}-deterministic QIVPM is
Impossible?}

To illustrate our proof for non-existence of $\delta$-deterministic
QIVPMs for $\delta<\frac{1}{3}$, we will explain why we cannot construct
any $\frac{1}{4}$-deterministic QIVPM in full details. The proof
is by contradiction: Suppose there is a $\frac{1}{4}$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. Now use this assumed
QIVPM to construct the following $0$-deterministic QIVPM $\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\tfrac{1}{4}\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[\tfrac{3}{4},1\right]\:.
\end{cases}
\end{equation}
However, since we know that $0$-deterministic QIVPMs do not exist~\cite{THOS2017},
the map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$
does not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$
is indeed a QIVPM by checking that for orthogonal projectors $P_{0}$
and~$P_{1}$, 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,\label{eq:QuantumInterval-valuedProbability-Equal}
\end{equation}
because similar to classical inclusion-exclusion principle, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
implies for each pair of commuting projectors $P_{0}$ and~$P_{1}$,
\begin{equation}
\begin{aligned} & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}^{\textrm{D}}\left(P_{0}P_{1}\right)\\
={} & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)\,,
\end{aligned}
\end{equation}
i.e., $\bar{\mu}^{\textrm{D}}$ is convex.

For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
and 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
\subseteq{} & \left[\tfrac{3}{4},1\right]+\left[0,\tfrac{1}{4}\right]=\left[\tfrac{3}{4},\tfrac{5}{4}\right]\,.
\end{aligned}
\end{equation}
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}
\end{figure*}
For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

@@

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs}Examples of $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ on commuting events $P$.}
\begin{tabular}{ccc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{A}(P)$  & $\bar{\mu}_{B}(P)$ \tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$  & $\imposs$ \tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\necess$  & $\left[\frac{3}{4},\frac{4}{5}\right]$ \tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\imposs$  & $\left[\frac{1}{5},\frac{1}{4}\right]$ \tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$  & $\necess$ \tabularnewline
\bottomrule
\end{tabular}
\end{table}

\noindent It is easy to construct $\delta$-deterministic classical
IVPMs $\bar{\mu}_{A}$ and $\bar{\mu}_{B}$ defined in Table~\ref{tab:classical-IVPMs},
where $\proj{0}$ and $\proj{1}$ represents heads and tails in coin-tossing,
respectively. The interpretation for $\bar{\mu}_{A}$ is that we have
a double-headed coin that always comes up heads. For $\bar{\mu}_{B}$,
the interpretation is that we throw a coin $1000$ times and we observe
$750$ heads and $200$ tails and the coin falls under the couch $50$
times. For $\bar{\mu}_{A}$, $\delta$ is $0$; for $\bar{\mu}_{B}$,
$\delta=\frac{1}{4}$, and $\delta$ qualifies how close a coin is
to double-headed (or double-tailed), which we can certainly know the
outcome of a coin even before tossing. We see here that we can construct
$0$-deterministic as well as $\frac{1}{4}$-deterministic and in
fact for any $\delta$ in the range $\left[0,1\right]$ we can construct
a $\delta$-deterministic classical probability measure. BUT the situation
changes in the quantum case, WE CANNOT construct $\delta$-deterministic
probability measures for $\delta<\frac{1}{3}$.

\section{Why a \texorpdfstring{$\frac{1}{3}$}{⅓}-deterministic QIVPM exists?}

\begin{table}
\noindent \centering{}\caption{\label{tab:classical-IVPMs-results}A sample experimental record for
a classical experiment with three possible outcomes $\proj{0}$, $\proj{1}$,
and $\proj{2}$. A event can be happened ($\happen$) or not happened
($\notHappen$), and the experimental results could be summarized
by a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.}
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:classical-IVPMs-results}}(P)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\proj{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\proj{1}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\proj{2}$ & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}-\proj{0}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}-\proj{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}-\proj{2}$ & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\end{table}
Sample experimental results with three possible outcomes $\proj{0}$,
$\proj{1}$, and $\proj{2}$ are listed in Table~\ref{tab:classical-IVPMs-results}.
Because the results of every event are always the same, they could
be summarized to a $0$-deterministic classical IVPM~$\bar{\mu}_{\ref{tab:classical-IVPMs-results}}$.
Given any Hilbert space of dimension~$d\ge3$, the Kochen-Specker
theorem asserts that we cannot have a table where every event always
has the same result~\cite{THOS2017}. 
\begin{table}
\noindent \centering{}\caption{\label{tab:quantum-IVPMs-results}A sample inconsistent experimental
record for a quantum experiment on a three-dimensional Hilbert space,
where $\proj{\psi}$ is any one-dimensional projector, and $\mathbb{1}-\proj{\psi}$
is any two-dimensional projector. A event can be happened ($\happen$)
or not happened ($\notHappen$), but $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}$
that summarizes the experimental results is not a QIVPM.}
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$P$  & Trial~0 & Trial~1 & Trial~2 & $\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}(P)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\proj{\psi}$  & $\notHappen$ & $\notHappen$ & $\notHappen$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}-\proj{\psi}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\happen$ & $\happen$ & $\happen$ & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\end{table}
For example, Table~\ref{tab:quantum-IVPMs-results} doesn't give
coherent experimental results, and cannot be summarized as a QIVPM
because given any two distinct one-dimensional projectors $P_{0}$
and $P_{1}$, 
\begin{equation}
\begin{aligned} & \bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}P_{1}\right)=\necess\\
\nsubseteq{} & \imposs=\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{0}\right)+\bar{\mu}_{\ref{tab:quantum-IVPMs-results}}\left(P_{1}\right)\,.
\end{aligned}
\end{equation}

### 2018-01-28 prop_prop_letter_ajhs_referee_response.tex

For orthogonal projectors~$P_{0}$ and $P_{1}$, when one of $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)$
and $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$ is $\necess$, say
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\necess$. Then, $\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
and 
\begin{equation}
\begin{aligned} & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\\
\subseteq{} & \left[\tfrac{3}{4},1\right]+\left[0,\tfrac{1}{4}\right]=\left[\tfrac{3}{4},\tfrac{5}{4}\right]\,.
\end{aligned}
\end{equation}
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is bounded by $\left[0,1\right]$,
we must have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{3}{4},1\right]$,
i.e., $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\necess=\bar{\mu}^{\textrm{D}}\left(P_{0}\right)+\bar{\mu}^{\textrm{D}}\left(P_{1}\right)$.

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}
\end{figure*}
For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

After we explained why there is no $\delta$-deterministic QIVPMs
for $\delta<\frac{1}{3}$, we are going to explain the physical meaning
of $\delta$-deterministic, and understand the transition from $\delta<\frac{1}{3}$
to $\delta\ge\frac{1}{3}$.

\section{Physical Meaning of $\delta$-Determinism}

Since QIVPMs are extensional of both quantum probability measures
and classical IVPMs, the meaning of $\delta$-determinism can be explained
better when we consider $\delta$-deterministic classical IVPMs.

\begin{definition}[$\delta$-Determinism for classical IVPMs]\label{def:delta-deterministic-classical}
Given a classical IVPM~$\bar{\mu}:\eventsC\rightarrow\mathscr{I}$,
where $\eventsC$ is the set of mutually commuting events. Then, $\bar{\mu}$
is $\delta$-deterministic if, for every event $P\in\events'$, we
have either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$. \end{definition}

### 2018-01-29 prop_prop_letter_ajhs_referee_response.tex

\begin{figure*}
\includegraphics[bb=50bp 100bp 900bp 300bp,clip,scale=0.5]{prop_prop_letter_ajhs_referee_response_pptx}\caption{\label{fig:Show-subset}Show $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$.}
\end{figure*}
For orthogonal projectors~$P_{0}$ and $P_{1}$, when $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\frac{1}{4}\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\frac{1}{2}\right]$.
Since $\bar{\mu}\left(P_{0}+P_{1}\right)$ is a subset of either $\left[0,\frac{1}{4}\right]$
or $\left[\tfrac{3}{4},1\right]$ and the latter is excluded as illustrated
in Fig.~\ref{fig:Show-subset} , then $\bar{\mu}\left(P_{0}+P_{1}\right)$
must be a subset of $\left[0,\frac{1}{4}\right]$, which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

After we explained why there is no $\delta$-deterministic QIVPMs
for $\delta<\frac{1}{3}$, we are going to explain the physical meaning
of $\delta$-deterministic, and understand the transition from $\delta<\frac{1}{3}$
to $\delta\ge\frac{1}{3}$.

\section{Physical Meaning of \texorpdfstring{$\delta$}{δ}-Determinism}

Since the definition of QIVPMs is a generalization of both classical
IVPMs and conventional quantum probability measures, the meaning of
$\delta$-determinism can be explained better when we consider $\delta$-deterministic
classical IVPMs.
